ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-21 pyked.tex
note in acks
added some software references for PyKED

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\usepackage[inline]{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

@@

@@

%====================================================================
\section{Acknowledgements}
This research was funded by \ldots
\todo[inline]{update}

>>>>

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\newcommand\pk{PyKED}
\usepackage[inline]{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

Fundamental combustion experiments provide

@@

\pk{} relies on well-established scientific Python software tools.
These include NumPy~\cite{vanderWalt:2011np} for array manipulation, Pint~\cite{Grecco2016} for
interpreting and converting between units, \texttt{ruamel.yaml} for parsing YAML files,\todo{needs ref}{}
Cerberus for validating \ck{} files\todo{needs ref}{},
and pytest~\cite{pytest:3.0.1} for unit testing.
Travis-CI~\cite{Travis2016} also provides continuous integration testing.

@@

%====================================================================
\section{Acknowledgements}
This research was funded by \ldots
\todo[inline]{update}
% Kyle: I don't think I have any funding yet to acknowledge for this
